% ============================================================
%  MASLD & Stroke Risk — Meta-Analysis Manuscript
%  Title: Metabolic dysfunction–associated steatotic liver disease
%         and stroke risk: A systematic review and meta-analysis
%         exploring AF-associated and fibrosis-related pathways
% ============================================================
\documentclass[12pt,a4paper]{article}

% ---- Packages ----
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{caption}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{setspace}
\doublespacing
\usepackage{lineno}
\linenumbers
\usepackage{fancyhdr}
\usepackage{hyperref}
\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}
\usepackage{natbib}
\bibliographystyle{unsrtnat}
\usepackage{xcolor}
% \usepackage{multirow}      % Not in BasicTeX — install if needed
% \usepackage{enumitem}     % Not in BasicTeX — install if needed

% ---- Metadata ----
\title{\textbf{Metabolic dysfunction--associated steatotic liver disease and stroke risk:\\
A systematic review and meta-analysis exploring AF-associated and fibrosis-related pathways}}

\author{
  % Authors to be filled
}

\date{July 1, 2026}

\begin{document}
\maketitle

% ============================================================
%  ABSTRACT
% ============================================================
\begin{center}
\textbf{Abstract}
\end{center}
\vspace{-8pt}

\textbf{Background:} Metabolic dysfunction--associated steatotic liver disease (MASLD) has been linked to increased cardiovascular risk, but its specific association with stroke — and the potential pathways underlying this association — remains incompletely characterized. We conducted a systematic review and meta-analysis to quantify the MASLD--stroke association and explore two candidate pathways: atrial fibrillation (AF) and hepatic fibrosis.

\textbf{Methods:} We searched [databases] for studies reporting stroke risk in MASLD versus non-MASLD populations. Random-effects meta-analysis was performed (REML estimator). Heterogeneity was explored via meta-regression (AF adjustment as moderator), subgroup analyses, and fibrosis-stratified estimates. Evidence for an AF-associated pathway was evaluated across five hierarchical levels (Table S1). Fibrosis-related risk was assessed through severity-stratified estimates and longitudinal fibrosis dynamics.

\textbf{Results:} Across 21 studies including approximately 29.8 million participants, MASLD was associated with a 37\% increased risk of stroke (HR 1.37, 95\% CI 1.28--1.46), with substantial heterogeneity (I\textsuperscript{2}=98.6\%). Meta-regression identified AF adjustment as a significant moderator: AF adjustment explains part of between-study heterogeneity (R\textsuperscript{2}=16.4\%, p=0.040), with predicted stroke risk attenuating from HR 1.40 (95\% CI 1.31--1.49) to HR 1.13 (95\% CI 0.93--1.37) after AF adjustment. Patient-level interaction analysis (Jang 2026) confirmed effect modification by baseline AF (without AF: HR 1.10; with AF: HR 1.03, 0.95--1.12). Among four studies reporting fibrosis-stratified estimates, higher fibrosis burden was consistently associated with greater stroke risk, with the strongest signal from NFS-based stratification (Chen 2023: advanced fibrosis HR 2.08). Fibrosis regression was associated with reduced stroke risk (Park 2022: HR 0.58) compared to persistent fibrosis (HR 1.31).

\textbf{Conclusions:} MASLD is associated with increased stroke risk. These findings support the existence of a potential AF-associated pathway linking MASLD and stroke risk; however, formal mediation cannot be established from the available evidence. Fibrosis severity and dynamics may provide prognostic information beyond AF. These observations highlight the potential value of AF surveillance and fibrosis assessment in MASLD patients for stroke risk stratification.

\newpage

% ============================================================
%  INTRODUCTION
% ============================================================
\section{Introduction}

Metabolic dysfunction--associated steatotic liver disease (MASLD), formerly known as non-alcoholic fatty liver disease (NAFLD), affects approximately 25--30\% of the global adult population and represents the hepatic manifestation of the metabolic syndrome \cite{}. While MASLD is strongly associated with cardiovascular morbidity and mortality, its specific relationship with cerebrovascular events — particularly stroke — has received less systematic attention.

Several mechanisms have been proposed to link MASLD with stroke risk. Atrial fibrillation (AF), which is more prevalent in MASLD patients, may represent one such pathway: MASLD-associated systemic inflammation, autonomic dysfunction, and atrial structural remodeling may promote AF, which in turn increases thromboembolic stroke risk. Hepatic fibrosis severity may independently contribute to a prothrombotic state through altered coagulation factor synthesis and endothelial dysfunction.

However, existing primary studies vary substantially in their adjustment for AF and assessment of fibrosis, contributing to marked between-study heterogeneity. We conducted this systematic review and meta-analysis to: (1) quantify the overall association between MASLD and stroke risk; (2) evaluate the evidence for an AF-associated pathway linking MASLD and stroke; and (3) characterize the relationship between hepatic fibrosis severity/dynamics and stroke risk.

% ============================================================
%  METHODS
% ============================================================
\section{Methods}

\subsection{Search Strategy and Selection Criteria}

A systematic review and meta-analysis was conducted in accordance with the Preferred Reporting Items for Systematic Reviews and Meta-Analyses (PRISMA 2020) guidelines. Electronic searches were performed in PubMed, Embase, Web of Science, and the Cochrane Library from database inception to [search date].

Search terms combined controlled vocabulary and free-text keywords related to metabolic dysfunction--associated steatotic liver disease and cerebrovascular outcomes, including ``MASLD'', ``MAFLD'', ``NAFLD'', ``fatty liver'', ``hepatic steatosis'', ``stroke'', ``cerebrovascular disease'', ``ischemic stroke'', and ``hemorrhagic stroke''. The detailed search strategy for each database is provided in Supplementary Material.

Studies were eligible if they: (1) included adult participants; (2) evaluated MASLD, MAFLD, or NAFLD as the exposure; (3) reported incident stroke or cerebrovascular events as outcomes; (4) provided hazard ratios (HRs), relative risks (RRs), or odds ratios (ORs) with corresponding 95\% confidence intervals (CIs), or sufficient data for calculation; and (5) used a cohort, case-control, or longitudinal observational design.

Studies were excluded if they: (1) lacked stroke-related outcomes; (2) did not provide effect estimates; (3) involved pediatric populations; (4) were reviews, editorials, conference abstracts, case reports, or animal studies; or (5) contained overlapping populations. When overlapping cohorts were identified, the largest or most comprehensive dataset was retained for quantitative synthesis. Specifically, Park et al. (2022) and Jang et al. (2026) originated from partially overlapping Korean National Health Insurance Service populations; therefore, only Jang et al. (2026) was included in the primary meta-analysis, whereas Park et al. (2022) was retained for descriptive evaluation of fibrosis dynamics.

Two investigators independently screened titles, abstracts, and full texts. Disagreements were resolved through discussion and consensus.

\subsection{Data Extraction and Quality Assessment}

Two investigators independently extracted study-level data using a standardized data collection form. Extracted variables included first author, publication year, country, study design, population characteristics, sample size, follow-up duration, MASLD/MAFLD/NAFLD definition, fibrosis assessment method, stroke outcome definition, covariate adjustment strategy, and reported effect estimates.

When multiple models were reported, the most fully adjusted estimate was preferentially extracted for quantitative synthesis. Hazard ratios (HRs) and corresponding 95\% confidence intervals (CIs) were used as the primary effect measures. Relative risks and odds ratios were considered equivalent to HRs because stroke incidence was generally low in the included populations.

Study quality was assessed using the Newcastle--Ottawa Scale (NOS) for cohort studies. The NOS evaluates three domains: participant selection, comparability of study groups, and outcome assessment. Studies scoring 7--9 points were considered high quality, 5--6 points moderate quality, and $<$5 points low quality.

Risk-of-bias assessments were independently performed by two investigators, with disagreements resolved by consensus. Overall certainty of evidence was further evaluated using the Grading of Recommendations Assessment, Development and Evaluation (GRADE) framework.

\subsection{Statistical Analysis}

The primary analysis used random-effects meta-analysis with restricted maximum-likelihood (REML) estimation to pool study-level hazard ratios, chosen to account for both within-study and between-study variability in observational data. Standard random-effects confidence intervals are reported for all primary and subgroup estimates. The Hartung--Knapp adjustment was applied as a sensitivity analysis to yield more conservative confidence intervals. Heterogeneity was quantified using I\textsuperscript{2} and Cochran's Q, with I\textsuperscript{2} values of 25\%, 50\%, and 75\% interpreted as low, moderate, and high heterogeneity, respectively. The between-study variance component ($\tau^2$) was estimated using REML.

\textit{Subgroup analyses.} Pre-specified subgroup analyses were performed to explore sources of heterogeneity. Studies were stratified by: (1) stroke outcome subtype (total stroke vs. ischemic stroke); (2) MASLD definition criteria (NAFLD, MAFLD, or MASLD); (3) AF adjustment status (adjusted vs. not adjusted); (4) fibrosis assessment status (assessed vs. not assessed); and (5) study setting (population-based vs. hospital/clinic-based). Subgroup differences were tested using a random-effects test for between-group heterogeneity, with a separate $\tau^2$ estimated for each subgroup.

\textit{Meta-regression.} Univariate random-effects meta-regression was performed to evaluate study-level covariates as moderators of the MASLD--stroke association. Covariates tested included: AF adjustment (binary), MASLD definition criteria (categorical), diagnosis method (categorical), country (categorical), follow-up duration (continuous), log-transformed sample size (continuous), and mean age (continuous). The proportion of between-study variance explained by each moderator was expressed as R\textsuperscript{2}, and statistical significance of moderators was assessed using the omnibus QM test.

\textit{AF-associated pathway analysis.} Evidence for an AF-associated pathway was evaluated using a five-level hierarchy: Level I — between-study meta-regression (AF adjustment as moderator); Level II — patient-level interaction by baseline AF status (Jang 2026); Level III — within-study AF covariate adjustment; Level IV — bundle adjustment for cardiovascular comorbidities including AF (Lee 2021); and Level S1 — supporting pathway evidence linking MASLD to incident AF (Ohno 2023). Attenuation of the excess risk attributable to AF was calculated as (HR\textsubscript{without AF} $-$ HR\textsubscript{with AF}) / (HR\textsubscript{without AF} $-$ 1) $\times$ 100\%.

\textit{Fibrosis-related pathway analysis.} Fibrosis-stratified stroke risk estimates were extracted from studies reporting fibrosis severity categories using histology or non-invasive scores (NFS, BARD, AAR). Given heterogeneity in fibrosis measurement methods, formal pooling across tools was not performed; individual-study estimates were presented descriptively. Fibrosis dynamics were evaluated using longitudinal data from Park et al. (2022), comparing stroke risk in participants with fibrosis regression versus persistent fibrosis.

\textit{Sensitivity analyses.} Robustness of the primary finding was assessed through: (1) leave-one-out analysis, iteratively omitting each study to evaluate its influence on the pooled estimate; (2) exclusion of Kim et al. (2020), the study with the largest effect estimate; (3) exclusion of Lee et al. (2025) and Kim et al. (2024), which shared NHIS source populations with other included studies; and (4) exclusion of all three studies simultaneously as the most conservative estimate. Baujat plots were generated to quantify each study's contribution to overall heterogeneity and influence on the pooled result.

\textit{Publication bias.} Publication bias was assessed using: (1) funnel plot symmetry with pseudo 95\% confidence limits; (2) Egger's linear regression test for funnel plot asymmetry; (3) Begg's rank correlation test; and (4) trim-and-fill analysis to estimate the number of potentially missing studies and the adjusted pooled estimate. Given the known sensitivity of publication-bias tests to a single influential study, Egger's test was repeated after exclusion of the largest study (Lee et al. 2025).

All analyses were conducted in R (version 4.5.2) using the \texttt{meta} package (version 8.5-0) for meta-analysis and subgroup analyses, and the \texttt{metafor} package (version 5.0-1) for meta-regression and sensitivity analyses. Statistical significance was set at $\alpha = 0.05$ (two-sided), with p-values between 0.05 and 0.10 considered borderline.

% ============================================================
%  RESULTS
% ============================================================
\section{Results}

\subsection{Study Characteristics and Main Analysis}

The systematic search identified 2,192 records, of which 1,615 were screened after deduplication, 590 underwent full-text review, and 21 studies met inclusion criteria for quantitative synthesis (PRISMA flowchart, Supplementary Figure S1). Study characteristics are summarized in Table 1. The 21 included studies encompassed approximately 29.8 million participants from 5 countries (predominantly South Korea, n=14), published between 2019 and 2025. Study designs included population-based nationwide cohorts (n=8) and hospital- or clinic-based cohorts (n=13). MASLD was defined using NAFLD (n=8), MAFLD (n=7), or MASLD (n=6) criteria, with FLI-based ultrasonography as the most common diagnostic method. Median follow-up ranged from 3.2 to 15.8 years. Two studies adjusted for atrial fibrillation (AF); seven studies assessed hepatic fibrosis (Supplementary Table S2).

Across 21 studies, MASLD was associated with a 37\% increased risk of stroke (random-effects HR 1.37, 95\% CI 1.28--1.46, p$<$0.001; common-effect HR 1.32, 95\% CI 1.31--1.33; Figure 2). Individual study hazard ratios ranged from 1.10 (Jang 2026) to 2.01 (Kim 2020), all exceeding 1.0. Substantial between-study heterogeneity was observed (I\textsuperscript{2}=98.6\%, $\tau^2$=0.022, Cochran's Q=1403.9, df=20, p$<$0.001).

\subsection{Subgroup Analyses}

Subgroup analyses by stroke subtype showed comparable risk estimates for total stroke (k=13, HR 1.34, 95\% CI 1.26--1.43) and ischemic stroke (k=8, HR 1.40, 95\% CI 1.21--1.60), with no significant between-group difference (p=0.62; Supplementary Figure S2).

By liver disease definition, pooled estimates were lower for MASLD-defined studies (k=6, HR 1.20, 95\% CI 1.12--1.29) than for NAFLD-defined (k=8, HR 1.42, 95\% CI 1.23--1.63) or MAFLD-defined studies (k=7, HR 1.41, 95\% CI 1.34--1.48; p-between=0.002; Supplementary Figure S7).

By AF adjustment status, studies without AF adjustment (k=19) yielded a pooled HR of 1.40 (95\% CI 1.30--1.50), whereas the two studies adjusting for AF yielded a substantially lower pooled estimate (k=2, HR 1.11, 95\% CI 1.07--1.16; p-between$<$0.001; Supplementary Figure S8). However, this subgroup comparison is limited by the small number of AF-adjusted studies.

By setting, population-based studies (k=8, HR 1.42, 95\% CI 1.23--1.64) and hospital/clinic-based studies (k=13, HR 1.33, 95\% CI 1.26--1.40) yielded comparable estimates (p-between=0.40; Supplementary Figure S10).

\subsection{Meta-Regression}

Of seven study-level covariates evaluated, only AF adjustment was a statistically significant moderator of between-study heterogeneity in meta-regression (R\textsuperscript{2}=16.4\%, p=0.040; $\beta = -0.214$; Figure 6A). MASLD definition criteria showed a numerically large but non-significant contribution (R\textsuperscript{2}=13.8\%, p=0.139). The remaining covariates — diagnosis method (R\textsuperscript{2}=0.0\%, p=0.68), country (R\textsuperscript{2}=0.0\%, p=0.92), follow-up duration (R\textsuperscript{2}=0.0\%, p=0.91), sample size (R\textsuperscript{2}=1.8\%, p=0.28), and mean age (R\textsuperscript{2}=6.9\%, p=0.25) — did not explain significant proportions of between-study variance (Supplementary Figures S4--S6).

\subsection{AF-Associated Pathway}

Evidence for an AF-associated pathway was evaluated using a five-level hierarchy (Supplementary Table S1).

\textit{Meta-regression (Level I).} Meta-regression identified AF adjustment as a significant moderator: AF adjustment explains part of between-study heterogeneity (R\textsuperscript{2}=16.4\%, p=0.040; $\beta = -0.214$; Figure 6A). The predicted stroke risk, estimated from the regression model, was HR 1.40 (95\% CI 1.31--1.49) without AF adjustment compared to HR 1.13 (95\% CI 0.93--1.37) with AF adjustment, corresponding to 67.7\% attenuation of the excess risk attributable to AF adjustment.

\textit{Interaction by baseline AF (Level II).} In the only study reporting AF-stratified individual-level estimates (Jang 2026), the association between MASLD and stroke remained significant among individuals without AF (HR 1.10, 95\% CI 1.08--1.11) but was attenuated among those with pre-existing AF (HR 1.03, 95\% CI 0.95--1.12; Figure 6B), consistent with effect modification by baseline AF status. Within-study AF covariate adjustment yielded consistent directional attenuation (HR 1.14 $\rightarrow$ 1.10; 28.6\% attenuation).

\textit{Supporting pathway evidence (Level S1).} Ohno et al. (2023) demonstrated that MASLD was associated with a 51\% increased risk of incident AF (HR 1.51, 95\% CI 1.46--1.57; n=8.2 million), establishing the MASLD--AF link in the proposed pathway.

\textit{Additional evidence.} Lee et al. (2021) reported attenuation after bundle adjustment for cardiovascular comorbidities including AF (HR 1.55 $\rightarrow$ 1.43; 21.8\%), though the AF-specific contribution could not be isolated.

\subsection{Fibrosis-Related Pathway}

Four studies reported fibrosis-stratified stroke risk estimates. Fibrosis assessment methods varied substantially across studies, ranging from histologic evaluation and validated fibrosis scores (NFS, BARD) to indirect biochemical surrogates such as the AST-to-ALT ratio (AAR). Individual study estimates are shown in Figure 7A. Across studies using histologic and non-invasive fibrosis assessment tools, higher fibrosis burden was consistently associated with greater stroke risk. The highest risk estimates were generally observed in advanced fibrosis categories, particularly when assessed by histology or NFS: histology (Simon 2022: low HR 1.50, intermediate HR 1.96, advanced HR 1.91), NFS (Chen 2023: low HR 1.29, intermediate HR 1.38, advanced HR 2.08), AAR (Chung 2022: reference HR 1.00, intermediate HR 1.13, high HR 1.29), and BARD (Jang 2026: low/reference HR 1.03, advanced HR 1.11).

Longitudinal fibrosis dynamics from Park et al. (2022) provided complementary evidence: fibrosis regression was associated with substantially reduced stroke risk (HR 0.58) compared to persistent fibrosis (HR 1.31; Figure 7B).

Although subgroup differences according to fibrosis assessment did not reach conventional statistical significance (p=0.078), studies evaluating more advanced fibrosis phenotypes tended to report higher risk estimates (Assessed: k=7, HR 1.26, 95\% CI 1.15--1.39; Not Assessed: k=14, HR 1.42, 95\% CI 1.30--1.55; Supplementary Figure S9). Exploratory pooled estimates by fibrosis severity category suggested higher stroke risk in advanced fibrosis compared with non-advanced fibrosis (Supplementary Material). Given the limited number of contributing studies (k=2--3 per category) and the heterogeneity in fibrosis measurement tools, these findings should be considered hypothesis-generating and interpreted with caution.

\subsection{Sensitivity Analyses and Publication Bias}

The association remained robust across sensitivity analyses. Excluding Kim 2020 — the study with the largest effect estimate — yielded a pooled HR of 1.34 (95\% CI 1.26--1.41; k=20). Excluding Lee 2025 and Kim 2024, which shared NHIS source populations, yielded HR 1.37 (95\% CI 1.27--1.47; k=19). Leave-one-out analysis confirmed that no single study drove the overall estimate.

Publication bias assessment was inconclusive. Egger's test was non-significant in the full sample (p=0.64) but became significant after excluding the largest study (Egger p=0.018 without Lee 2025). Begg's rank correlation test was non-significant (p=1.00). Funnel plot asymmetry emerged after removal of Lee 2025, warranting cautious interpretation (Supplementary Figure S3). Trim-and-fill analysis imputed three potentially missing studies; the adjusted pooled estimate remained significant (HR 1.31, 95\% CI 1.21--1.42), representing only a modest attenuation from the primary estimate (HR 1.37), suggesting that potential publication bias was unlikely to materially alter the overall conclusion.

The 95\% prediction interval for the primary estimate ranged from 1.01 to 1.84 (metafor), indicating that the true effect in a new study is expected to remain in the positive direction, although the lower bound approached unity. Taken together with the sensitivity and publication-bias analyses, the primary finding was considered robust.

% ============================================================
%  DISCUSSION
% ============================================================
\section{Discussion}

This systematic review and meta-analysis of 21 studies including approximately 29.8 million participants demonstrates that MASLD is associated with a 37\% increased risk of stroke. Beyond confirming this association, our analysis identifies two factors that contribute to risk heterogeneity: an AF-associated pathway and fibrosis severity/dynamics.

Meta-regression identified adjustment for atrial fibrillation (AF) as a significant source of between-study heterogeneity: AF adjustment explains part of the observed variance (R\textsuperscript{2}=16.4\%, p=0.040). Studies adjusting for AF generally reported lower effect estimates than those without AF adjustment, with predicted stroke risk attenuating from HR 1.40 to 1.13 after AF adjustment. This between-study finding is corroborated by patient-level interaction data (Jang 2026: HR 1.10 without baseline AF vs 1.03 with AF) and supported by large-scale evidence linking MASLD to incident AF (Ohno 2023: HR 1.51, n=8.2M). Taken together, these findings support the existence of a potential AF-associated pathway linking MASLD and stroke risk. However, formal mediation cannot be established using aggregate-level data; the between-study meta-regression is ecological by design. While several lines of evidence support an AF-associated pathway, individual-participant mediation analyses are warranted to further clarify the causal contribution of AF. We therefore describe this as an ``AF-associated pathway'' rather than confirming AF mediation.

One possible explanation for the observed AF-associated heterogeneity is that AF represents a competing cerebrovascular pathway that is variably accounted for across studies. Studies not adjusting for AF may capture both direct vascular effects of MASLD and AF-related embolic risk, whereas AF-adjusted models may isolate the residual risk independent of clinically recognized arrhythmia. This may explain why AF adjustment systematically attenuated the observed association across studies.

Regarding fibrosis, across studies using histologic and non-invasive fibrosis assessment tools, higher fibrosis burden was consistently associated with greater stroke risk. The highest risk estimates were observed in advanced fibrosis categories, particularly when assessed by histology or NFS (e.g., Chen 2023: advanced fibrosis HR 2.08). Advanced fibrosis may reflect cumulative exposure to systemic inflammation, endothelial dysfunction, prothrombotic activity, and adverse cardiometabolic remodeling. Therefore, fibrosis severity may serve not only as a marker of liver injury but also as an integrated indicator of long-term vascular risk. The dynamic nature of fibrosis-related risk — fibrosis regression associated with substantially reduced stroke risk (HR 0.58) compared to persistent fibrosis (HR 1.31) — further suggests that hepatic fibrosis may represent a modifiable risk modifier rather than a static confounder. The observation that fibrosis regression was associated with substantially lower stroke risk compared with persistent fibrosis extends the clinical relevance of these findings beyond risk prediction: these results suggest that fibrosis may represent a potentially modifiable determinant of cerebrovascular risk in MASLD, and that interventions targeting fibrosis regression may have cerebrovascular benefits beyond their hepatic indications. Most included studies used FLI-based definitions of steatosis rather than fibrosis assessment tools; consequently, fibrosis-specific analyses were restricted to studies employing histology or validated fibrosis scores such as NFS and BARD.

Importantly, fibrosis-associated stroke risk remained evident even after adjustment for AF in Jang et al. (2026), suggesting that fibrosis-related cerebrovascular risk may not be fully explained by AF-associated mechanisms. These findings support a model in which AF-related and fibrosis-related pathways contribute independently to stroke risk in MASLD. However, although subgroup differences according to fibrosis assessment showed a consistent direction (assessed: HR 1.26; not assessed: HR 1.42), they did not reach conventional statistical significance (p=0.078), and the heterogeneity in fibrosis measurement methods (histology, NFS, AAR, BARD) precludes formal meta-analytic pooling. Although exploratory pooled estimates suggested progressively higher stroke risk with greater fibrosis burden, the limited evidence base precludes definitive conclusions regarding a quantitative fibrosis--stroke gradient.

Because AF-related factors explained only part of the observed heterogeneity (R\textsuperscript{2}=16.4\%), additional mechanisms are likely involved. Potential pathways include systemic inflammation, endothelial dysfunction, prothrombotic activity, and accelerated atherosclerosis, all of which have been linked to advanced liver fibrosis and adverse vascular outcomes. The substantial residual heterogeneity (I\textsuperscript{2}=98.6\% even after accounting for AF) further underscores the multifactorial nature of the MASLD--stroke association.

Several limitations warrant consideration. First, the between-study meta-regression (Level I evidence) is ecological by design and cannot establish individual-level mediation. Second, only two studies in our sample adjusted for AF, limiting the statistical power of subgroup comparisons. Third, fibrosis-stratified estimates derive from single studies using non-standardized tools; fibrosis assessment methods varied substantially, with indirect surrogates such as the AST-to-ALT ratio carrying weaker evidentiary weight than histology or validated scores such as NFS. Fourth, residual confounding by metabolic comorbidities shared between MASLD and stroke cannot be excluded. Fifth, although formal publication-bias tests were negative in the full dataset, asymmetry became more apparent after exclusion of the largest study; trim-and-fill analysis suggested that the association remained significant after accounting for potential missing studies (HR 1.31, 95\% CI 1.21--1.42). Sixth, substantial statistical heterogeneity was observed (I\textsuperscript{2}=98.6\%), which is common in large-scale observational meta-analyses and reflects genuine between-study differences in populations, exposure definitions, and adjustment strategies rather than a failure of the meta-analytic approach. Despite this heterogeneity, several features support the robustness of the primary finding: the 95\% prediction interval remained above unity (1.01--1.84), indicating that the direction of association is expected to remain positive in future settings; all 21 individual study estimates exceeded 1.0; and sensitivity analyses yielded consistent results across exclusion criteria.

This study provides two major advances beyond previous MASLD--stroke meta-analyses. First, it identifies AF-related factors as a measurable contributor to between-study heterogeneity and integrates multiple levels of evidence supporting an AF-associated pathway. Second, it highlights fibrosis severity and fibrosis dynamics as clinically relevant determinants of stroke risk, suggesting that stroke risk in MASLD may not be static but potentially modifiable.

In conclusion, MASLD is associated with increased stroke risk. AF-associated mechanisms and fibrosis severity/dynamics represent potential contributors to risk heterogeneity. These findings support AF surveillance and fibrosis assessment as components of stroke risk stratification in MASLD patients.

% ============================================================
%  REFERENCES
% ============================================================
\newpage
\begin{thebibliography}{99}

% References will be added via BibTeX or manually

\end{thebibliography}

% ============================================================
%  FIGURE LEGENDS
% ============================================================
\newpage
\section*{Figure Legends}

\textbf{Figure 2.} Forest plot of the association between MASLD and stroke risk (main analysis). Random-effects meta-analysis (REML estimator), k=21, n$\approx$29.8M. Squares represent study-specific hazard ratios; size is proportional to study weight. Diamond represents the pooled estimate (HR 1.37, 95\% CI 1.28--1.46). I\textsuperscript{2}=98.6\%.

\textbf{Figure 6.} Evidence supporting an AF-associated pathway linking MASLD and stroke risk. \textbf{(A)} Meta-regression evidence: predicted hazard ratios from random-effects meta-regression with AF adjustment as moderator (R\textsuperscript{2}=16.4\%, p=0.040). Diamond vertices indicate predicted HRs and 95\% CIs. \textbf{(B)} Patient-level AF subgroup interaction (Jang 2026): dual forest plot without causal arrows. Effect modification annotation replaces directional arrow notation. \textbf{(C)} Left: mechanism cascade (MASLD $\rightarrow$ incident AF $\rightarrow$ stroke risk). Right: evidence chain boxes (meta-regression, AF subgroup interaction, MASLD$\rightarrow$AF pathway link).

\textbf{Figure 7.} Fibrosis severity and dynamics. \textbf{(A)} Fibrosis-stratified stroke risk estimates across assessment tools ranging from histology and validated scores (NFS, BARD) to indirect biochemical surrogates (AAR). Despite differences in fibrosis assessment methods, histologic and non-invasive fibrosis measures demonstrated a generally consistent direction of association with stroke risk. Shape coding: circle = low/reference, square = intermediate, triangle = advanced/high. Color coding by assessment tool. \textbf{(B)} Fibrosis dynamics (Park 2022): fibrosis regression (HR 0.58, protective) vs persistent fibrosis (HR 1.31).

\textbf{Supplementary Table S1.} Evidence hierarchy for the AF-associated pathway between MASLD and stroke risk. Five evidence levels: I (between-study meta-regression), II (patient-level interaction), III (within-study AF adjustment), IV (bundle adjustment), S1 (supporting pathway evidence). Attenuation calculated as (HR\textsubscript{without AF} $-$ HR\textsubscript{with AF}) / (HR\textsubscript{without AF} $-$ 1) $\times$ 100\%.

\textbf{Supplementary Figure S9.} Subgroup analysis by fibrosis assessment status (assessed vs not assessed). Random-effects model. p-between = 0.078.

\end{document}
